The Controlled Choice Design and Paternalism in Pawnshop Borrowing

### 2023-05-02 OA.tex
cdf analysis of tut(x)

\begin{figure}[H]
    \caption{Partitoin of TuT \& ToT effect by behavioral variables.}
    \label{tut_beh_partition}
    \begin{center}
    \begin{subfigure}{0.475\textwidth}
        \caption{TuT}
        \centering
        \includegraphics[width=\textwidth]{Figuras/tut_beh_partition.pdf}
    \end{subfigure}
    \begin{subfigure}{0.475\textwidth}
        \caption{ToT}
        \centering
        \includegraphics[width=\textwidth]{Figuras/tot_beh_partition.pdf}
    \end{subfigure}

@@

\begin{figure}[H]
    \caption{Predictors of commitment contract take-up}
    \label{interactions_takeup}
    \begin{center}
    \begin{subfigure}{0.45\textwidth}
        \caption{with Fee Arm}
        \centering
        \includegraphics[width=\textwidth]{Figuras/pago_frec_vol_fee_interactions_rf.pdf}
    \end{subfigure}
    \begin{subfigure}{0.45\textwidth}
        \caption{with Promise Arm}
        \centering
        \includegraphics[width=\textwidth]{Figuras/pago_frec_vol_promise_interactions_rf.pdf}
    \end{subfigure}
    \end{center}
     \scriptsize
      %\footnotesize{ \textit{Do file: }  \texttt{analyze\_fvp.do}}
\end{figure}

\scriptsize 
\noindent This figure reports bivariate regressions of the form $\widehat{TakeUp} = \alpha + \beta \: X_i + \epsilon_i$, where $\widehat{TakeUp}$ is the prediction using random forests. The figure reports the $\beta$ coefficients for different $X_i$'s along with 95\% confidence intervals. Panel (a) focuses on take up in the arm where clients could chose among the fee-commitment contract and the status quo contract. Panel (b) focuses on the arm where clients could chose among the promise-commitment contract and the status quo contract. Using random forests we can predict who takes up the fee-forcing contract with 85\% accuracy out of sample.\footnote{Correcting for the fact that most chose the status-quo contract using the method of SMOTE, \cite{smote} we find an accuracy rate of 75\%.} Which suggests that choice among contracts is not purely random. This figure shows that the more educated, those that report that their family typically asks for money, those that make a monthly budget of expenses, and those that ask for a remainder of their due payments (and marginally those we classify as present-biased) are more likely to chose the fee-commitment contract if given the choice. The opposite holds for clients that are more economically vulnerable (can barely pay for food, electricity, etc) and those that report being more stressed.

>>>>

\begin{figure}[H]
    \caption{Partition of TuT \& ToT effect by behavioral variables.}
    \label{tut_beh_partition}
    \begin{center}
    \begin{subfigure}{0.475\textwidth}
        \caption{TuT}
        \centering
        \includegraphics[width=\textwidth]{Figuras/tut_beh_partition.pdf}
    \end{subfigure}
    \begin{subfigure}{0.475\textwidth}
        \caption{ToT}
        \centering
        \includegraphics[width=\textwidth]{Figuras/tot_beh_partition.pdf}
    \end{subfigure}

@@

\begin{figure}[H]
    \caption{Predictors of commitment contract take-up}
    \label{interactions_takeup}
    \begin{center}
    \begin{subfigure}{0.45\textwidth}
        \caption{PLM}
        \centering
        \includegraphics[width=\textwidth]{Figuras/determinants_takeup_reg.pdf}
    \end{subfigure}
    \begin{subfigure}{0.45\textwidth}
        \caption{Logit}
        \centering
        \includegraphics[width=\textwidth]{Figuras/determinants_takeup_logit.pdf}
    \end{subfigure}
    \end{center}
     \scriptsize
      %\footnotesize{ \textit{Do file: }  \texttt{determinants_takeup.do}}
\end{figure}

\scriptsize 
\noindent This figure reports bivariate (and multivariate) regressions of the form $TakeUp = \alpha + \beta \: X_i + \epsilon_i$. The figure reports the $\beta$ coefficients for different $X_i$'s along with 95\% confidence intervals. Panel (a) uses a linear model. Panel (b) specifies a logit model.

### 2023-05-02 donde.tex
cdf analysis of tut(x)

\title{The limits of self-commitment and private paternalism \thanks{We want to thank Mauricio Romero and Anett John for advice and encouragement. Ricardo Olivares, Gerardo Melendez, and Alonso de Gortari provided excellent research assistance and Erick Molina helped with formatting. Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, David Laibson, Aprajit Mahajan, Matt Rabin, Charlie Sprenger, and seminar participants at ITAM provided valuable feedback.}}
\author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Francis J.\ DiTraglia   \thanks{Seira: ITAM/MSU, \url{enrique.seira@gmail.com} (corresponding author); McIntosh:  University of California San Diego, \url{ctmcintosh@ucsd.edu}; Meza: Harvard University, \url{isaacmezalopez@g.harvard.edu}; Sadka: ITAM, \url{jsadka@itam.mx}; DiTraglia: Oxford, \url{francis.ditraglia@economics.ox.ac.uk}} }
\date{This draft:  \today \\[2 cm]}

@@

In the context of pawnbroker lending, we show that forcing people into commitment contracts with financial penalties for not paying on time \textit{decreases} their (fee-including) financial cost by 9.4\%, increases the likelihood of recovering their pawn by 26\%, and increases the likelihood of repeat business by almost 100\%. Using machine learning methods for estimating heterogeneous treatment effects, we find that more than {70}\% clients would reduce their financing cost with the commitment contract, however only 10\% choose it. Those that \textit{don't} choose it are predicted to be the ones who would benefit more. Relying on personal promises instead of fees as commitment triples take-up but has no effects on outcomes.

@@

Although the examples above are plausible, substantiating a case for private paternalism is not easy. It involves comparing the causal effect of forcing a certain product characteristic versus the effect of letting people choose on that characteristic. This is not an easy task because a given person wither has or does not have choice, and because choice induces selection, potentially biasing causal estimates. A large behavioral literature has illustrated that allocating borrowers to a commitment-savings product increase savings \citep{thaler2004save, prina2015banking, brune2016facilitating, callen2019headwaters, Pascaline, Ashraf}, but this literature does not show that commitment would not be chosen by those that would benefit from it, that is, that the Treatment Effect on the Untreated (TuT) is positive. In fact, selection on gains has such wide acceptance that economists often impose it in their models \hl{CITES}. In microfinance, a context close to ours, \citep{Murdoch} claim that there exists positive selection, citing a positive correlation between displaying present biased preferences in surveys and selecting into microfinance as evidence of borrowers' actually demanding the discipline imposed by frequent payments. However, they are unable to show that borrowers indeed benefit or that they indeed positively select based on treatment effects.

@@

This paper studies the benefits of restricting choice in the context of pawnbroker lending. Pawn loans are one of the oldest, most understudied, and most prevalent forms of borrowing \citep{carter2012pawnshops}. There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues (in China it is a 43 billion dollar industry).\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner pawn lender (henceforth Lender $P$) alone served more than 1 million clients in the last 3 years with more than 4 million contracts.\footnote{For comparison there were 2.3 million micro-finance clients in Mexico in 2009 (\cite{Pedroza:2010}).} Pawnshop lending presents an inverted lending case: since these loans are over-capitalized, the principal in the lending contract stands to gain the most when agents default.

@@

The combination of voluntary and forced commitment within the RCT allows us to address several key questions.  First, does using more structured repayment contracts help pawnshop borrowers to save on financing cost. Second, do borrowers recognize this benefit, demanding commitment in sufficient numbers?  Finally, and most uniquely, because we incorporate the forced commitment arm, we are able to ask whether the \textit{right} borrowers voluntarily demand commitment, gaining point identification for the Treatment on the Treated (ToT) and the Treatment on the Untreated (TuT), using the control, choice, and forced arms.

@@

The monthly payment contract seems to be achieving these cost savings by speeding up payments and by generating an early bifurcation of borrowers into those that will recover the pawn and those that will not, saving the later payments towards recovery. In the treatment group, the first payment occurs 13 days earlier, the fraction recovering on the first visit by is 7.9 percentage point higher. Commitment contract decreases fraction of borrowers making a payment and not recovering by 7 percentage points. \hl{Treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery. That is, the commitment contract induces people who would otherwise pay something towards recovery, to pay more and faster, making them more likely to recover their pawn at a lower financial cost.}

@@

\hl{We start by bounding the distribution of treatment effects $Y_{1i}-Y_{0i}$ using the two marginal distribution } in the treatment and control arms as in \cite{fan2010sharp}. We find that at least 30\% of individual borrowers benefit from commitment, implying many borrowers did not demand even though the treatment effect would be positive for them. Then, we impose the mild exclusion restriction that the effect of the contract does not depend on how they got it, that is: choosing a contract has the same treatment effect as being assigned to the contract.\footnote{This is a frequently used assumption even if often implicit. For instance, a significant literature uses schooling compulsory laws to estimate the return of one more year of school, and then often interprets that schooling, in general, has this return.} We show that in this case our 3-armed experiment point identifies the TuT. We then estimate that the financial cost savings of the TuT is large, at \$356 pesos, equivalent to 24 percentage point savings in APR. That is, on average borrowers that did \textit{not} choose the frequent payment contract would have benefited from having that contract.\footnote{We estimate a positive ToT that is larger than the TuT, but it is imprecise\footnote{This results from the smaller sample size, given that few chose the monthly payment contract.}, and the hypothesis of ToT=TuT is rejeted only with 13 percent confidence for the APR and 12 percent confidence for default.}  We also estimate that those that would not choose if given the opportunity would have lower status-quo outcomes (i.e. the average selection bias is negative). Finally, assuming the exclusion restriction for subsets of observable characteristics splits generated by a causal forest allows us to establish that \hl{70\%} of would-be non-choosers would save on financial cost by being assigned to frequent payments. That is, the benefits of imposing a monthly payment are distributed broadly. \hl{TuT benefits are particularly large for XXX CHARACTERISTICS, and ToT benefits for those with XXX.}

\textcolor{brown}{In a final step, we use the Causal Random Forest algorithm of \cite{atheygrf} to estimate individual-level treatment effects for the forced versus control arm, and show the benefits of forcing to be significantly negatively correlated with the propensity to choose commitment estimated from the choice arm.  93\% of those who did not opt for the commitment contract would have been better off with it, while only 1\% of those who chose commitment would have been better off without it.} \textcolor{blue}{Targeting frequent payment products to those that benefit the most is a policy that should be explored. In this context we calculate \hl{XXX}.}

@@

What explains the persistence of a contract so contrary to borrowers’ interests?  First, we show substantial levels of over-optimism among borrowers.  Those most likely to benefit from the commitment contract and \textit{not} choose it are the individuals who most systematically over-estimate their own probability of repayment at the time of taking the loan.\footnote{More generally \hl{demand for commitment is higher among those with XXX characteristics.}}  Second, the existence of commitment-style repayment contracts in pawnshop lending is novel in Mexico. The dramatic improvements in borrower income arising from the commitment contract come directly from the pockets of lenders, reinforcing that the pawn industry as a whole has a strong interest in retaining the status quo.

Does learning eventually overcome the low demand for commitment? For learning to happen clients would need to experiment the frequent payment contract, and this was not the typical contract in the industry. But even if the contract was experienced, borrower may fail to learn or learn only slowly. We find that those who are forced to the monthly payment product are 6.7 percentage points more likely to become repeat costumers than those assigned to the status-quo contract. One way to interpret this is that that having experienced the frequent payment contract (and the lower financial cost of borrowing that come with it), they want to borrow more.\footnote{A second intepretation is that the iliquidity created by the monthly payment contract makes them want obtain second loan to pay the first one. This second explanation is unlikely since borrowers obtain a second loan not within the first 90 days of the first loan when payments are due; moreover, the correlation is also present conditional on having paid down the first loan. Borrowers tend to pledge a different piece for the second loan, so that recovery of the first pawn is also an unlikely explanation.} However, a stronger test of liking the monthly payment contract is whether conditional on coming again, they would choose frequent payments. We test this and we cannot reject that demand is not higher after experiencing the monthly payment contract, however sample sizes are small and \hl{the minimum detectable effect is XXX.}

@@

Our results suggest that pawn lending markets capture borrower wealth in ways not well summarized by interest rates. By overcollateralizing and then structuring loan contracts in a manner encouraging of default, lenders are able to extract substantial value independent of the interest charged.  Further, the `nudge’ approach generally favored by the behavioral literature (voluntary commitment) may not be adequate. We hesitate to give precise policy recommendations since we don't have good measures of welfare. Even though the monthly payment contract dramatically reduces financial cost, it could potentially generate lower (or higher) anxiety. Moreover, frequent payment requirements may decrease welfare of highly impatient borrowers.\footnote{The paper presents an back of the envelope exercise that suggests annual discount rates of 4000 are necessary to nullify the reductions in financial cost we estimate. \hl{Note also that since the fee for skipping payment is 2\%, the iliquidity imposed by the contract is bounded.}} %Second, given the non-standard nature of the finding, it is likely that we would have to adopt and estimate a particular behavioral model of demand for commitment, which we don't need to do to make the point that TuT is positive.

@@

Our paper speaks to several strands of the literature.   %First, they suggest consequential ways in which different financial services draw client pools with distinct behavioral biases. 
First, to research in microfinance studying the effect of payment frequency.  While research in microfinance markets has not found the same benefits from providing a more regularized repayment environment \citep{Pande}, those experiments are performed on top of highly structured contracts and among borrower pools who may have selected into that type of lending precisely because it provides structure. This may explain why there is almost no default in the control group in \citep{Pande}. Second, we broaden the analysis of the extent to which voluntary commitment mechanisms are taken up and effective.  Like our study, commitment demand has been found to be low in a number of contexts (\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}). Other papers have found more robust demand for commitment (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}). But unlike all these papers we can point identify the benefit the non-takers would have had if they had taken up and the benefit for the takers, and thus can talk more rigorously about private paternalism in this context.

@@

Two recent papers that shed some light into private paternalism. In the context of food choice, \cite{Sprenger} elicit dynamic inconsistencies, and then find that demand for commitment is negatively correlated with such inconsistency. In the context of school choice, \cite{Walters} finds that students that select into more effective schools have smaller treatment effects from attending than those that select out. Besides being very different contexts from ours, we rely on very different methods. In contrast to \cite{Sprenger} we will directly point identify the TuT, obviating the need for elicitation of preferences to test for negative selection. In contrast to \cite{Walters} we use randomization while he needs a structural model and distance to school as an instrument. \hl{FRANK, can I say something more precise than ``a structural model''?}

Methodologically we contribute to the large literature on treatment effect heterogeneity by showing how an experimental design with two forcing arms and one choice arm allows for identification of the ToT, the TuT and other important parameters under minimal assumptions. \cite{aronow2013beyond} and \cite{angrist2013extrapolate} assume no selection on gains to estimate \hl{XXX}. \cite{Walters} achieve identification of the TuT by using parametric model and a distance instrument, which requires the model to be correct and the instrument to be valid. TUT and ATE implied by LATE-and-re-weight differ sharply from his model-based estimates. The method of 
\cite{heckman2007econometric} and \cite{cornelissen2018benefits} require the availability of instrumental variable with rich support, and separability of observed and unobserved determinants of treatment effects.

>>>>

\title{The controlled choice design and private paternalism in pawnshop borrowing\thanks{We want to thank Mauricio Romero and Anett John for advice and encouragement. Ricardo Olivares, Gerardo Melendez, and Alonso de Gortari provided excellent research assistance and Erick Molina helped with formatting. Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, David Laibson, Aprajit Mahajan, Matt Rabin, Charlie Sprenger, and seminar participants at ITAM, USC, and UCSD provided valuable feedback.}}
\author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Francis J.\ DiTraglia   \thanks{Seira: ITAM/MSU, \url{enrique.seira@gmail.com} (corresponding author); McIntosh:  University of California San Diego, \url{ctmcintosh@ucsd.edu}; Meza: Harvard University, \url{isaacmezalopez@g.harvard.edu}; Sadka: ITAM, \url{jsadka@itam.mx}; DiTraglia: Oxford, \url{francis.ditraglia@economics.ox.ac.uk}} }
\date{This draft:  \today \\[2 cm]}

@@

In the context of pawnbroker lending, we show that forcing people into commitment contracts with a regular repayment structure decreases their (fee-including) financial cost by 6\%, increases the likelihood of recovering their pawn by 15\%, and increases the likelihood of repeat business by 20\%.  Using a multi-armed RCT that includes both a voluntary and a forced arm, we illustrate how to point-identify both the Treatment on the Untreated and the Treatment and the Treated.  We find modest selection on gains but nonetheless significant positive benefits of commitment even for those who would not have chosen it.  The justification for paternalistic commitment in this context appears to be over-optimism; 74\% of clients say they will certainly recover their pawn while in fact only 43\% do so.

%In the context of pawnbroker lending, we show that forcing people into commitment contracts with financial penalties for not paying on time \textit{decreases} their (fee-including) financial cost by 9.4\%, increases the likelihood of recovering their pawn by 26\%, and increases the likelihood of repeat business by almost 100\%. Using machine learning methods for estimating heterogeneous treatment effects, we find that more than {70}\% clients would reduce their financing cost with the commitment contract, however only 10\% choose it. Those that \textit{don't} choose it are predicted to be the ones who would benefit more. Relying on personal promises instead of fees as commitment triples take-up but has no effects on outcomes.

@@

Substantiating a case for private paternalism is not easy. It involves comparing the causal effect of forcing a certain product characteristic versus the effect of letting people choose it. This is not a straightforward task because choice will be driven by unobservable factors, and to address the question fully we would want a counterfactual for the outcome of both choosers and non-choosers. A large behavioral literature has illustrated that allowing borrowers or savers to choose commitment-style products increase savings in an Intention-to-Treat sense \citep{thaler2004save, prina2015banking, brune2016facilitating, callen2019headwaters, Pascaline, Ashraf}, but this literature has rarely inquired about the benefits of imposing commitment.\footnote{Selection on gains has such wide acceptance that economists often impose it in their models (for example, in the study of migration \cite{chiquiar2005international} and occupational choice \cite{heckman1990empirical}. In microfinance, a context close to ours, \citep{Murdoch} claims that positive selection exists, citing a positive correlation between displaying present biased preferences in surveys and selecting into microfinance as evidence of borrowers' actually demanding the discipline imposed by frequent payments.}   In this paper we illustrate how a three-armed, `controlled choice' design can be used to form counterfactuals for both choosers and non-choosers of commitment, providing a high-stakes and policy-relevant environment in which to test selection-on-gains as well as isolating the impact of paternalistic policies.

@@

Here we study the benefits of private paternalism in the context of pawnbroker lending. Pawn loans are one of the oldest, most understudied, and most prevalent forms of borrowing \citep{carter2012pawnshops}. There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues (in China it is a 43 billion dollar industry).\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner pawn lender (henceforth Lender $P$) alone served more than 1 million clients in the last 3 years with more than 4 million contracts.\footnote{For comparison there were 2.3 million micro-finance clients in Mexico in 2009 (\cite{Pedroza:2010}).} Pawnshop lending presents an inverted lending case: since these loans are over-capitalized, the principal in the lending contract stands to gain the most when agents default.

@@

We call this randomization of voluntary and forced commitment a controlled choice design, and it allows us to address several key questions.  First, does using more structured repayment contracts help pawnshop borrowers to save on financing cost. Second, do borrowers recognize this benefit, demanding commitment in sufficient numbers?  Finally, and most uniquely, because we incorporate the forced commitment arm, we are able to ask whether the \textit{right} borrowers voluntarily demand commitment, gaining point identification for the Treatment on the Treated (ToT), the Treatment on the Untreated (TuT), and the average selection on gains.

@@

The monthly payment contract seems to be achieving these cost savings by speeding up payments and by generating an early bifurcation of borrowers into those that will recover the pawn and those that will not, saving the later payments towards recovery. In the treatment group, the first payment occurs 13 days earlier, the fraction recovering on the first visit by is 7.9 percentage point higher. Commitment contract decreases fraction of borrowers making a payment and not recovering by 7 percentage points. Treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery. Instead, the commitment contract induces people who would otherwise pay something towards recovery to pay more and faster, as well as inducing others who would have made partial payments and anyways defaulted to instead pay nothing.  Both groups save money.

@@

We start by bounding the distribution of individual treatment effects as in \cite{fan2010sharp} and find that at least 30\% of individual borrowers benefit from commitment, implying many borrowers did not demand even though the treatment effect would be positive for them. Then, we impose the twin exclusion restrictions necessary for estimation of the ToT and Tut (that the effect of choosing or not choosing is the same as being assigned or not assigned the contract).\footnote{This is a frequently used assumption even if often implicit. For instance, a significant literature uses schooling compulsory laws to estimate the return of one more year of school, and then often interprets that schooling, in general, has this return.}  With these assumptions, both treatment effects are point identified as well as the average selection on gains, average selection on levels, and average selection bias.  Our results indicate that while selection on gains are present in our sample, the financial cost savings of the TuT is still large (at \$356 pesos, it is equivalent to 24 percentage point savings in APR). Hence, on average borrowers that did \textit{not} choose the frequent payment contract would have benefited from having that contract.\footnote{While our estimated ToT is roughly twice the TuT, it is imprecisely estimated due to the low compliance rate, and the hypothesis of ToT=TuT is rejected only with 13 percent confidence for the APR and 12 percent confidence for default.}  We also estimate that those that would not choose if given the opportunity would have lower status-quo outcomes (i.e. the average selection bias is negative). Finally, assuming the exclusion restriction for subsets of observable characteristics splits generated by a causal forest allows us to establish that more than \hl{70\%} of would-be non-choosers would save on financial cost by being assigned to frequent payments. That is, the benefits of imposing a monthly payment are distributed broadly. \hl{TuT benefits are particularly large for XXX CHARACTERISTICS, and ToT benefits for those with XXX.}

%\textcolor{brown}{In a final step, we use the Causal Random Forest algorithm of \cite{atheygrf} to estimate individual-level treatment effects for the forced versus control arm, and show the benefits of forcing to be significantly negatively correlated with the propensity to choose commitment estimated from the choice arm.  93\% of those who did not opt for the commitment contract would have been better off with it, while only 1\% of those who chose commitment would have been better off without it.} \textcolor{blue}{Targeting frequent payment products to those that benefit the most is a policy that should be explored. In this context we calculate \hl{XXX}.}

@@

What explains the persistence of a contract so contrary to borrowers’ interests?  First, we investigate whether simple impatience could explain the dissonance (our formula for financial does not use discounting, and the contract features near-term costs in return for longer-term benefits).  A simple simulation exercise suggests that at discount rates up to 4,000 percent per annum our core impacts on financial cost remains significantly negative, suggesting that discounting is unlikely to explain our results.  Next, we look at time inconsistent preferences, the workhorse behavioral explanation for the benefits of commitment.  In our context, not only is time inconsistency only a weak driver of selection into commitment, but the TuT of forcing commitment arises almost entirely among those who are \textit{not} time inconsistent.  In this pawnbroking sample we document substantial levels of over-optimism among borrowers, the attribute which we believe explains our results.  Not only do 74\% of borrowers say that they will recover their pawn with perfect certainty (whereas only 43\% actually do), but the impact of forcing on those who would not choose commitment is almost perfectly confined to the sub-sample who reported sure confidence in recovery.   Hence, in this context it appears that the explanation for low demand for commitment among those who benefit arises from an incorrect belief that one has no need to work to avoid default.

%Those most likely to benefit from the commitment contract and \textit{not} choose it are the individuals who most systematically over-estimate their own probability of repayment at the time of taking the loan.\footnote{More generally \hl{demand for commitment is higher among those with XXX characteristics.}}  Second, the existence of commitment-style repayment contracts in pawnshop lending is novel in Mexico. The dramatic improvements in borrower income arising from the commitment contract come directly from the pockets of lenders, reinforcing that the pawn industry as a whole has a strong interest in retaining the status quo.

%do we want this paragraph on learning?
Does learning eventually overcome the low demand for commitment? For learning to happen clients would need to experiment the frequent payment contract, and this was not the typical contract in the industry. But even if the contract was experienced, borrowers may fail to learn or learn only slowly. We find that those who are forced to the monthly payment product are 6.7 percentage points more likely to become repeat customers than those assigned to the status-quo contract. One way to interpret this is that that having experienced the frequent payment contract (and the lower financial cost of borrowing that come with it), they want to borrow more.\footnote{A second intepretation is that the iliquidity created by the monthly payment contract makes them want obtain second loan to pay the first one. This second explanation is unlikely since borrowers obtain a second loan not within the first 90 days of the first loan when payments are due; moreover, the correlation is also present conditional on having paid down the first loan. Borrowers tend to pledge a different piece for the second loan, so that recovery of the first pawn is also an unlikely explanation.} However, a stronger test of liking the monthly payment contract is whether conditional on coming again, they would choose frequent payments. We test this and we cannot reject that demand is not higher after experiencing the monthly payment contract, however sample sizes are small and \hl{the minimum detectable effect is XXX.}

@@

%Replace this paragraph with discussion of optimal targeting of paternalism
Our results suggest that pawn lending markets capture borrower wealth in ways not well summarized by interest rates. By over-collateralizing and then structuring loan contracts in a manner encouraging of default, lenders are able to extract substantial value independent of the interest charged.  Further, the `nudge’ approach generally favored by the behavioral literature (voluntary commitment) may not be adequate. We hesitate to give precise policy recommendations since we don't have good measures of welfare. Even though the monthly payment contract dramatically reduces financial cost, it could potentially generate lower (or higher) anxiety. Moreover, frequent payment requirements may decrease welfare of highly impatient borrowers.\footnote{The paper presents an back of the envelope exercise that suggests annual discount rates of 4000 are necessary to nullify the reductions in financial cost we estimate. \hl{Note also that since the fee for skipping payment is 2\%, the iliquidity imposed by the contract is bounded.}} %Second, given the non-standard nature of the finding, it is likely that we would have to adopt and estimate a particular behavioral model of demand for commitment, which we don't need to do to make the point that TuT is positive.

@@

Our paper speaks to several strands of the literature.   First, we contribute methodologically to the large literature on treatment effect heterogeneity by showing how an experimental design with two forcing arms and one choice arm allows for identification of the ToT, the TuT and other important parameters under minimal assumptions.  A large literature inspired by \cite{heckman1979sample} and \cite{angrist1996identification} has used an exclusion restriction to instrument for the LATE; rarer are studies that have compared forcing to choice to instrument for the TUT (such as looking at compulsory high school requirements \citep{oreopoulos2006estimating}, and one at technology that defaults individuals into variable pricing of electricity \citep{fowlie2021default}.  When the three arms (control, choice, and forcing) are randomized in the same environment we gain a clear and policy-relevant window into how selection into treatment relates to heterogeneity in treatment effects.  This comparison of treatment effects across the compliance distribution is closely related to the evaluation of Marginal Treatment Effects, and hence speaks to the large observational literature using parametric assumptions and continuous instruments to estimate MTEs , such as \cite{heckman2007econometric} and \cite{cornelissen2018benefits}, and \cite{Walters}.

%\cite{aronow2013beyond} and \cite{angrist2013extrapolate} assume no selection on gains to estimate \hl{XXX}. \cite{Walters} achieve identification of the TuT by using parametric model and a distance instrument, which requires the model to be correct and the instrument

Second, we join a more nacent literature shedding light into private paternalism. In the context of food choice, \cite{Sprenger} elicit dynamic inconsistencies, and then find that demand for commitment is negatively correlated with such inconsistency. In the context of school choice, \cite{Walters} finds that students that select into more effective schools have smaller treatment effects from attending than those that select out. Besides being very different contexts from ours, we rely on very different methods. In contrast to \cite{Sprenger} we will directly point identify the TuT, obviating the need for elicitation of preferences to test for negative selection. In contrast to \cite{Walters} we use randomization while he needs a structural model and distance to school as an instrument. \hl{FRANK, can I say something more precise than ``a structural model''?}

Finally, our results speak to the financial literature that examines the effect of contract structure on repayment.  While research in microfinance markets has not found the same benefits from providing a more regularized repayment environment \citep{Pande}, those experiments are performed on top of highly structured contracts and among borrower pools who may have selected into that type of lending precisely because it provides structure. This may explain why there is almost no default in the control group in \citep{Pande}. Second, we broaden the analysis of the extent to which voluntary commitment mechanisms are taken up and effective.  Like our study, commitment demand has been found to be low in a number of contexts (\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}). Other papers have found more robust demand for commitment (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}). But unlike all these papers we can point identify the benefit the non-takers would have had if they had taken up and the benefit for the takers, and thus can talk more rigorously about private paternalism in this context.

@@

### 2023-05-02 presentation.tex
cdf analysis of tut(x)

\title{The Controlled Choice Design and Paternalism in Pawnshop Borrowing? \\
Preliminary --comments welcome}
\author{Craig McIntosh\inst{1} \and Isaac Meza\inst{2} \and Joyce Sadka\inst{3} \and Enrique Seira\inst{4} \and Francis J. DiTraglia\inst{5} }
\institute[UTran]{\inst{1} UCSD, \inst{2} Harvard , \inst{3} ITAM , \inst{4} MSU , \inst{5} Oxford}

@@

   \vfill   \item Key quantity in debate about paternalism:  impacts on those who wouldn't elect to take the program versus impacts on those that do.  %How do treatment effects relate to selection?

@@

\section{Outline}
\begin{frame}{Outline}
     \begin{itemize}
         \vfill\item \textbf{Experimental Design}
         \vfill\item Main results
         \vfill\item Paternalism (...working on it)
     \end{itemize}
\end{frame}

@@

\begin{frame}{Outline}
     \begin{itemize}
         \vfill\item Experimental Design
         \vfill\item \textbf{Main results}
         \vfill\item Paternalism (...working on it)
     \end{itemize}
\end{frame}

@@

@@

\vspace{.4in}
    \centering Working on this...
\end{frame}

@@

\begin{frame}{Predictors of take-up : $\Pr(Take-up)$}

>>>>

\title{The Controlled Choice Design and Paternalism in Pawnshop Borrowing}
\author{Craig McIntosh\inst{1} \and Isaac Meza\inst{2} \and Joyce Sadka\inst{3} \and Enrique Seira\inst{4} \and Francis J. DiTraglia\inst{5} }
\institute[UTran]{\inst{1} UCSD, \inst{2} Harvard , \inst{3} ITAM , \inst{4} MSU , \inst{5} Oxford}

@@

   \vfill   \item Key quantity in debate about paternalism:  impacts on those who wouldn't elect to take the program versus impacts on those that do.   \begin{itemize}
       \item Oreopoulos 2006: effect of mandatory high school laws.
       \item Fowlie et al. 2021: defaulting customers into variable electricity pricing.
   \end{itemize}

   %How do treatment effects relate to selection?

@@

\section{Outline}
\begin{frame}{Outline}
     \begin{itemize}
         \vfill\item \textbf{Experimental Design}
         \vfill\item Main results
         \vfill\item Paternalism
     \end{itemize}
\end{frame}

@@

\begin{frame}
\textbf{Predictors of take-up : $\Pr(Take-up)$}

\begin{frame}{Outline}
     \begin{itemize}
         \vfill\item Experimental Design
         \vfill\item \textbf{Main results}
         \vfill\item Paternalism 
     \end{itemize}
\end{frame}

@@

    \label{choose_wrong}

        \begin{figure}{\textwidth}
        \caption{Mistakes in choice arm}
        \centering
        \includegraphics[width=0.65\textwidth]{Figuras/line_cw_apr_tot_tut.pdf}
        \end{figure}

\begin{itemize}
    \item   Use Random Forest to estimate ToT, TUT conditional on covariates.
    \item $>$ 70\% of non-choosers would have seen some benefit from assignment to commitment.
    \item  $<$ 20\% of choosers made a mistake.
\end{itemize}

@@

@@
